\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color,xcolor}
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{00008B}
\definecolor{shade}{HTML}{D4D7FE}      %light blue shade
\definecolor{text1}{HTML}{000000}      %text is black
\definecolor{headings}{HTML}{00008B}   %navy blue
\hypersetup{   colorlinks,breaklinks,
               urlcolor=linkcolor,
               linkcolor=linkcolor
}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Joseph Randall Hunt}  & 650.690.0657 (phone)\\
144 Avonlea Pl &  randallhunt@gmail.com\\
Johnson City, TN  37604& http://www.ranman.org/\\
\end{tabular*}
\\

\vspace{0.1in}
\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Western Carolina University}{Cullowhee, NC}{B.S., Computer Science (Grades: 80\%)}{Aug. 2009 - May. 2012}
	\begin{itemize}
		\resitem{Relevant courses: Data Structures, Software Engineering, Wireless Sensor Networks, Internet Security and Ethics, Computer Graphics, Calculus, Discrete Mathematics, Statistics, Computer Networking, Computer Organization}
	\end{itemize}
\item
	\ressubheading{Punahou Academy}{Honolulu, HI}{High School}{2005-2009}
	\begin{itemize}
		\resitem{Graduated with Honors. Deans' list every year. One of four seniors out of 400 selected for special recognition by the faculty. High scores on SAT/ACT/AP exams.}
	\end{itemize}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{SpotOn}{New York, NY}{Software Engineer}{May 2011 - Oct. 2011}
	\begin{itemize}
		\resitem{Designed and implemented a collaborative filtering recommendation engine in Python and C which improved recommendation speed by \%300. Used SciPy and NumPy to dramatically increase speed.}
		\resitem{Wrote scripts to automate deployment and logging of Amazon Web Services. Used the boto Python framework.}
		\resitem{Designed and coded the company landing page.}
	\end{itemize}
\item
   \ressubheading{NASA Ames Research Center}{Mountain View, CA}{Software Engineer}{Jan. 2011 - May. 2011}
   \begin{itemize}
      \resitem{Created an Automatic KML Tour Generator and KML Tour Editor using Django, Python, SQL, and Javascript. Media import tool pulls from several different sources and loads all data into a database. Project generated a whole new set of data products for the Maps team.}
   \end{itemize}
\item
   \ressubheading{NASA Langley Research Center}{Hampton, VA}{Software Engineer}{May 2010 - Aug. 2010}
      \begin{itemize}
         \resitem{Worked on several tools for mass properties evaluation
         which culminated in the design a mass properties API. Also worked
         with an 8 person team to design and evaluate a series of tests on
         a flotation concept. If implemented project could save millons of
         dollars. Findings were published to NASA's main webpage, AIAA 
         newsletter, and several other notable websites.}
      \end{itemize}
\item
   \ressubheading{Western Carolina University}{Cullowhee, NC}{Various Roles}{Aug. 2009 - May 2011}
      \begin{itemize}
         \resitem{Resolved IT issues for students and faculty. Also taught several workshops on web development.}
         \resitem{Assisted professor and students in introductory computer science courses as a TA.}
         \resitem{Maintained the computer science lab computers running Linux, Windows, and OSX with several VMs. Created scripts to automatically update and backup all computers and all VMs. Managed backups leading to a \%5 decrease in downtime from previous administrator.}
      \end{itemize}
\end{itemize}
\pagebreak
\resheading{Skills}
\begin{description}
\item[Languages:]
C, Java, Python, Javascript, PHP, Ruby, Prolog, HTML/CSS, SQL, LISP, MIPS, Objective-C, French, German, Spanish
\item[Systems/Tools:]
OS X, Linux (CentOS, Gentoo, Ubuntu, Debian), Windows, MySQL, MongoDB, vim, emacs, xcode
\item[Frameworks/APIs:]
jQuery, node, processing, pyramid, django, SciPy, NumPy, Foursquare, Facebook, Google (maps, translate, docs, etc.), cocoa, ant, jUnit
\end{description}

\resheading{Honors/Awards/Presentations}
\begin{itemize}
   \item Third Place HackNY Fall 2011 Hackathon (out of 25 teams and 150 competitors)
   \item HackNY Fellow (one of 35 students selected to intern at NYC startups)
   \item Deans List, Honors College
   \item Featured in Honor's College ``Imagine'' magazine
   \item Only student representative on Academic Technology Committee
   \item AP Scholar's Award
   \item Several presentations at NASA
\end{itemize}
\resheading{Activities and Societies}
\begin{itemize}
   \resitem{IEEE Member}
   \resitem{\href{http://polaris.cs.wcu.edu/~acm/}{Student ACM Chapter}}
   \resitem{\href{https://github.com/ranman}{Open-Source Contributor}}
   \resitem{Active on 
      \href{http://stackoverflow.com/users/240004/ranman}
   {StackOverflow}}
   \resitem{Passionate about Robotics
      \href{http://robotics.punahou.edu/}{[1]}
      \href{http://irg.arc.nasa.gov}{[2]}}
   \resitem{\href{http://www.youtube.com/user/ranman96734}{Rubik's Cubes}}
\end{itemize}
\resheading{Coursework and Independent Projects}
\begin{itemize}
   \resitem{\href{http://www.mosaicmachine.com/}{Mosaic Machine}}
   \resitem{\href{http://www.locreep.com/}{LoCreep}}
   \resitem{Multiuser Chat System in Java}
   \resitem{Set Associative Cache Simulator in Java}
   \resitem{Tokenizer and Parser in C}
   \resitem{Wireless Sensor Grapher in TinyC+Java}
   \resitem{TCP Implementation in TinyC}
   \resitem{Adventure Game in Prolog}
\end{itemize}
\pagebreak

\resheading{References}
Please contact me. This document is hosted online and I would prefer not to reveal my former employer's contact information.
\end{document}