\chapter{Conclusion}\label{chap:conclusion}
While this document is by no means complete it provides a good starting point for a profile that needs to be completed for my computer science degree. To summarize the content thus-far I can say that I have a good grasp of low level systems and the essential programming abstractions involved in those systems. What does this mean to a prospective employer? It means my code will be to a standard above that of the average code-monkey. I'll understand exactly how it is executing and behaving all the way down to the CPU. It means that I can work with new microprocessors and architectures with relatively little training.

My time at Western, though brief so far, has been one of the most informative experiences of my life. One thing I have learned is that a computer scientist's skills do not lay solely in the technical realm. While I can do the math and solve the programming problems, I believe the most essential skill for a computer scientist is the ability to understand complex multi-tiered abstractions and the ability to pick up knowledge from any area of study very quickly. A computer scientist is not just a machine that churns out code. A computer scientist is a person deserving of their title ``scientist'': they know how to research, they know basic science from several fields, and they're fully cognizant of how their program will interact or contribute to the overall product or experiment. So, as a prospective employer, you should ask yourself if all of your candidates posses the same non-technical skills that I do.
